\newpage
\lecture{12}{2021-12-01}{Design Questions}

\section*{Customer Price Sensitivity}
\begin{itemize}
  \item Online retailers, such as Amazon, has the advantage of adjusting "shelf" prices easily to determine people's individual price (in)sensitivities.
        \begin{itemize}
          \item Columns: 2000 most popular products
          \item Rows: Customers
          \item Entries:
                \begin{itemize}
                  \item 0: Customer hasn't bought.
                  \item 1: Customer bought at \textbf{lowest} price.
                  \item 2: '' \textbf{midranged} ''.
                  \item 3: '' \textbf{highest} ''.
                \end{itemize}
        \end{itemize}
  \item How to predict price insensitivity?
  \item Cluster so that price insensitive people are farther away from the origin. (e.g., 3s vs 0s).
  \item To make prediction easier, consider designing a label. How? Row sum divided by \# of non-zero entries.
  \item What type of clustering?
        \begin{itemize}
          \item K-means? Nah, groups seem more like onion slices rather than blobs
          \item EM? Reasoning for clusters makes sense.\@ e.g., frugal, middle, cash money. So should expect 3 reasonable groups
                \begin{itemize}
                  \item Spoiler: It does!
                \end{itemize}
          \item Density? Nah. Nothing alludes to density based clusters.
          \item Hierarchical? Too many rows (large amount of data), and we don't care about the fine details.
          \item SVD? Maybe. 2k dimensional space into 3d space.
                \begin{itemize}
                  \item Sometimes doesn't reveal clusters with clean separation.
                \end{itemize}
        \end{itemize}
  \item Prediction (based on new label):
        \begin{itemize}
          \item Baye's Rule? Too many attributes.
          \item kNN? Might be good based on EM clustering results.
          \item NN? Nope, a lot of attributes and data and attributes may not be related to each other.
          \item SVM? Meh.
          \item RF? Probably!
                \begin{itemize}
                  \item Pretty accurate!
                \end{itemize}
        \end{itemize}
\end{itemize}

\section*{Outline for an answer}
\begin{itemize}
  \item An answer. We can design a way to calculate the price insensitivity by first designing a label (details). One digression has an issue (mention it). Another digression, all products aren't created equal. So we'll weight the score function based on the average of a attribute and the std dev of the column sums. Then talk about \textbf{clustering} to help decide on a predictor and analyze other properties of the dataset. Argue for appropriate clustering methods and why others aren't reasonable.\@ e.g., ones that are clearly good or clearly bad. Then talk about predictors in a similar manner. Then talk about actionable tasks from design. Continue to mention digressions to aim for that A+.
  \item Comment on weaknesses (i.e., digressions) to suggested approaches and think of alternatives/further improvements to get an A+.
\end{itemize}
